---
output: pdf_document
author: "AFCEC"
params: 
    set_title: "My Title!"
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

---
title: `r paste0(installationName,"Missing Data Report")`
---

```{r, echo=FALSE,message=FALSE,error=FALSE,warning=FALSE}
Sys.setenv(PATH = paste(Sys.getenv("PATH"), "C:\\Program Files\\MiKTeX 2.9\\miktex\\x64\\bin", sep=.Platform$path.sep))
suppressWarnings(suppressPackageStartupMessages(library(ggplot2)))
suppressWarnings(suppressPackageStartupMessages(library(dplyr)))
suppressWarnings(suppressPackageStartupMessages(library(leaflet)))
suppressWarnings(suppressPackageStartupMessages(library(DT)))
suppressWarnings(suppressPackageStartupMessages(library(stringr)))
library(knitr)
library(markdown)
library(rmarkdown)
library(rgdal)
library(sf)
library(devtools)
library(Rcpp)
library(kableExtra)
```

```{r, echo=FALSE,message=FALSE,error=FALSE,warning=FALSE}
Overview <- sf::st_read(dsn = installationGDB, layer = "Overview",quiet=TRUE)
MissingFDS <- sf::st_read(dsn = installationGDB, layer = "MissingFDS",quiet=TRUE)
MissingFCs <- sf::st_read(dsn = installationGDB, layer = "MissingFCs",quiet=TRUE)
EmptyFeatureClasses <- sf::st_read(dsn = installationGDB, layer = "EmptyFeatureClasses",quiet=TRUE)
Determinant_Values_by_FC <- sf::st_read(dsn = installationGDB, layer = "Determinant_Values_by_FC",quiet=TRUE)
NullCellCountbyFC <- sf::st_read(dsn = installationGDB, layer = "NullCellCountbyFC",quiet=TRUE)
TBDCellCountbyFC <- sf::st_read(dsn = installationGDB, layer = "TBDCellCountbyFC",quiet=TRUE)
OtherCellCountbyFC <- sf::st_read(dsn = installationGDB, layer = "OtherCellCountbyFC",quiet=TRUE)
MissingData <- sf::st_read(dsn = installationGDB, layer = "MissingData",quiet=TRUE)


```
# Summary

1. `r Overview$MissingFDScount` : Total Number of Missing Feature Datasets   
2. `r Overview$MissingFCcount` : Total Number of Missing Feature Class (within included Feature Datasets)  
3. `r Overview$TotalMissingFields` : Total Number of Missing Fields (within included Feature Classes  
4. `r nrow(MissingFCs)` : Total Number of Missing Feature Classes   
5. `r Overview$InclFeatsEmpty` : Total Number of Feature Classes Empty (within included Feature Datasets)  
6. `r Determinant_Values_by_FC$InclFeatsEmpty` : Total Number of Feature Classes Empty (within included Feature Datasets)  
7. `r sum(MissingData$TOTAL_INTD_COUNT)` : Total number of cells are missing data (i.e.: 'Null', 'TBD', or 'Other')   
8. `r sum(MissingData$NULL_FC_COUNT)` : Total number of cells are 'Null' data   
9. `r sum(MissingData$TBD_FC_COUNT)` : Total number of cells are 'TBD' data   
10. `r sum(MissingData$OTHER_FC_COUNT)` : Total number of cells are 'Other' data   

# What's included in this packet?

An overview of Null data found in your geodatabase.

## Missing Feature Datasets

Within `r installationName`'s geodatabase, a total of `r nrow(MissingFDS)` Feature Datasets are not included. The 'Missing Feature Datasets' table gives a listing of all the Feature Datasets missing.

## Missing Feature Classes
Of the Feature Datasets properly included in `r installationName`'s geodatabase,`r nrow(MissingFCs)` are not present. The 'Missing Feature Classes' table gives a listing of all the Feature Classes missing, along with the associated Feature Dataset.


## Included, but Empty, Feature Classes
Of the Feature Classes properly included,`r Overview$InclFeatsEmpty` are empty. The 'Included, but Empty, Feature Classes' table gives a listing of all the included, but empty, Feature Classes in `r installationName`'s geodatabase.


## Counts of Determined and Indetermined Feature Classes
Within the correctly

## Null Count by Feature Class

## Other Cell Count by Feature Class

## TBD Cell Count by Feature Class



\pagebreak



# Missing Feature Datasets
```{r, echo=FALSE,message=FALSE,error=FALSE,warning=FALSE}
MissingFDS<-MissingFDS[ , -which(names(MissingFDS) %in% c("INSTALLATION"))]
kable(MissingFDS, booktabs = T, caption = "Missing Feature Datasets")

```



\pagebreak

# Included, but Empty, Feature Classes 
```{r, echo=FALSE,message=FALSE,error=FALSE,warning=FALSE}
EmptyFeatureClasses<-EmptyFeatureClasses[ , -which(names(EmptyFeatureClasses) %in% c("INSTALLATION","TOTAL_EMPTY_FIELDS"))]
kable(EmptyFeatureClasses, booktabs = T, caption = "Empty Feature Classes")

```


\pagebreak


# Missing Feature Classes
```{r, echo=FALSE,message=FALSE,error=FALSE,warning=FALSE}
MissingFCs<-MissingFCs[ , -which(names(MissingFCs) %in% c("INSTALLATION"))]
MissingFCs<-MissingFCs[,c("FDS","FC_MISSING")]
kable(df, booktabs = T, caption = "Missing Feature Classes")
```




\pagebreak



# Percent of Values Not 'Null', 'TBD', or 'Other'

```{r, echo=FALSE,message=FALSE,error=FALSE,warning=FALSE}
Determinant_Values_by_FC<-Determinant_Values_by_FC[ , -which(names(Determinant_Values_by_FC) %in% c("INSTALLATION","TOTAL_DET_COUNT","TOTAL_INTD_COUNT"))]
colnames(Determinant_Values_by_FC)[3] <- "Values_Determinated(%)"
Determinant_Values_by_FC$`Values_Determinated(%)`<-Determinant_Values_by_FC$`Values_Determinated(%)`*100
Determinant_Values_by_FC$`Values_Determinated(%)`<-round(Determinant_Values_by_FC$`Values_Determinated(%)`,digits=1)

kable(Determinant_Values_by_FC,  booktabs = T, caption = "Count of Null Cells by Feature Class") %>%
kable_styling(latex_options = c("repeat_header", "scale_down")) %>%
landscape()

```


\pagebreak



# 'Null' Count by Feature Class
```{r, echo=FALSE,message=FALSE,error=FALSE,warning=FALSE}
NullCellCountbyFC<-NullCellCountbyFC[ , -which(names(NullCellCountbyFC) %in% c("INSTALLATION"))]
kable(NullCellCountbyFC, longtable = T, booktabs = T, caption = "Count of Null Cells by Feature Class") %>%
kable_styling(latex_options = c("repeat_header", "scale_down"))


```


\pagebreak



# 'TBD' Count by Feature Class
```{r, echo=FALSE,message=FALSE,error=FALSE,warning=FALSE}
TBDCellCountbyFC<-TBDCellCountbyFC[ , -which(names(TBDCellCountbyFC) %in% c("INSTALLATION"))]
kable(TBDCellCountbyFC, longtable = T, booktabs = T, caption = "Count of Null Cells by Feature Class") %>%
kable_styling(latex_options = c("repeat_header", "scale_down"))


```




\pagebreak



# 'Other' Count by Feature Class
```{r, echo=FALSE,message=FALSE,error=FALSE,warning=FALSE}
OtherCellCountbyFC<-OtherCellCountbyFC[ , -which(names(OtherCellCountbyFC) %in% c("INSTALLATION"))]
kable(OtherCellCountbyFC, longtable = T, booktabs = T, caption = "Count of Null Cells by Feature Class") %>%
kable_styling(latex_options = c("repeat_header", "scale_down"))


```
